Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-19 doc/mc-paper.tex
fix negation statement

The monolithic approach
takes advantage of the clausal representations of
the input formula $\inputformula$ and the POG formula $\phi_\noder$.
It can
express the negation of $\phi_\noder$ as $\neg \phi_\noder = \bigcup_{\nodeu\in P} \simplify{\theta_{u}}{\{\obar{r}\}}$.
Forward implication
will hold
when $\inputformula \imply \phi_\noder$, or  equivalently,
that the formula $\inputformula \land \neg \phi_\noder$
is unsatisfiable, where the
conjunction can be expressed as the union
of the two sets of clauses.  The proof generator writes the clauses to a file and invokes a proof-generating SAT solver.
For each clause $C$ in the unsatisfiability proof, it adds clause $\{r\} \cup C$ to the CRAT proof, and so the empty clause in the proof becomes the unit clause $r$.
Our experimental results show
that this approach can be very effective and generates short proofs
for smaller problems, but it does not scale well enough for routine
use.

>>>>

The monolithic approach
takes advantage of the clausal representations of
the input formula $\inputformula$ and the POG formula $\phi_\noder$.
We can express the negation of $\phi_\noder$ in clausal form as
$\theta_{\obar{\noder}} = \bigcup_{\nodeu\in P} \simplify{\theta_{u}}{\{\obar{r}\}}$.
Forward implication will hold when $\inputformula \imply \phi_\noder$, or  equivalently
when the formula $\inputformula \land \theta_{\obar{\noder}}$
is unsatisfiable, where the
conjunction can be expressed as the union
of the two sets of clauses.  The proof generator writes the clauses to a file and invokes a proof-generating SAT solver.
For each clause $C$ in the unsatisfiability proof, it adds clause $\{r\} \cup C$ to the CRAT proof, and so the empty clause in the proof becomes the unit clause $r$.
Our experimental results show
that this approach can be very effective and generates short proofs
for smaller problems, but it does not scale well enough for routine
use.
